---
title: "Homework4"
author: "Hivansh Dhakne"
output: pdf_document
date: "2023-10-24"
---

# Problem 1
```{r}
data <- read.table("C:\\Users\\hivan\\Downloads\\d_logret_6stocks.txt", header = TRUE)
intel_logret <- data$Intel
Pfizer_logret <- data$Pfizer
```
## (a)
```{r}
t_test <- t.test(intel_logret, mu = 0)
t_test
```
Reject the null hypothesis

## (b)
```{r}
wilcoxon_test <- wilcox.test(intel_logret, mu = 0, paired = FALSE)
wilcoxon_test
```
Fail to reject the null hypothesis

## (c)
```{r}
t_test_unequal <- t.test(intel_logret, Pfizer_logret, var.equal = FALSE)
t_test_unequal
```
Fail to reject the null hypothesis

## (d)
```{r}
t_test_equal <- t.test(intel_logret, Pfizer_logret, var.equal = TRUE)
t_test_equal
```
Fail to reject the null Hypothesis

## (e)
```{r}
wilcoxon <- wilcox.test(intel_logret, Pfizer_logret, paired = FALSE)
wilcoxon
```
Fail to reject the null hypothesis

## (f)
```{r}
f <- var.test(intel_logret, Pfizer_logret)
f
```
Fail to reject the null hypothesis

# Problem 2
```{r}
line1 <- c(1.18, 1.42, 0.69, 0.88, 1.62, 1.09, 1.53, 1.02, 1.19, 1.32)
line2 <- c(1.72, 1.62, 1.69, 0.79, 1.79, 0.77, 1.44, 1.29, 1.96, 0.99)
```

## (a)
```{r}
t_test <- t.test(line1, line2, var.equal = TRUE)
conf_int <- t_test$conf.int
p_value <- t_test$p.value

conf_int
p_value
```

## (b)
```{r}
t_test <- t.test(line1, line2, var.equal = FALSE)
conf_int <- t_test$conf.int
p_value <- t_test$p.value

conf_int
p_value
```
There is no statistical significance at 0.05

# Problem 3
```{r}
affected_eye <- c(488, 478, 480, 426, 440, 410, 458, 460)
unaffected_eye <- c(484, 478, 492, 444, 436, 398, 464, 476)
```

## (a)
```{r}

t_test <- t.test(affected_eye, unaffected_eye, conf.level = 0.90)
p_value <- t_test$p.value

t_test
```
Fail to reject the null hypothesis. There is no evidence of a difference in corneal thickness.

## (b)
```{r}
conf_interval <- t_test$conf.int
conf_interval[1]
conf_interval[2]

```


